---
title: "Italian tick viromes - Data analysis and figures"
author: "Andrea Silverj"
date: '2023-11-14'
output: html_document
---

# -----[Data visualization]-----

-|Taxonomic classification|-

Super-kingdom
Kingdom
Phylum
Class
Order
Family
Genus
Species

Set working directory and load libraries:
```{r message=FALSE, warning=FALSE}
setwd("C:/Users/silverja/Projects/tickvirome/Analysis")
library("ggplot2")
library("tidyverse")
library("dplyr")
library("purrr")
library("RColorBrewer")
library("ComplexHeatmap")
library("DescTools")
library("circlize")
library("readxl")
library("writexl")
library("stringr")
library("ggExtra")
library("cowplot")
library("ggtree")
library("ips")
library("treeio")
library("tidytree")
library("ggimage")
library("ggnewscale")
library("phytools")
library("phangorn")
library("extrafont")
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")
library("mapproj")
library("raster")
library("maptools")
library("stars")
library("sf")
library("rgdal")
library("raster")
library("vegan")
theme_set(theme_bw())

```

Set functions
```{r}
# Generic functions
outersect <- function(x, y) {
  sort(c(setdiff(x, y),
         setdiff(y, x)))
}

reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
  new_x <- paste(x, within, sep = sep)
  stats::reorder(new_x, by, FUN = fun)
}

scale_x_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
}

metric_names <- list("shannon"="Shannon","simpson"="Inverse Simpson")
metric_labeller <- function(variable,value){
  return(metric_names[value])
}

# Define functions for alpha diversity calculation
# Richness
richness <- function(x){
  sum(x>0)
}
# Shannon index
shannon <- function(x){
  rabund <- x[x>0]/sum(x)
  -sum(rabund * log(rabund))
}
# Simpson index
simpson <- function(x){
  n <- sum(x)
  sum(x * (x-1) / (n * (n-1)))
}
```

Import data
```{r}
# Table with sample stats
sample_stats <- data.frame(read.csv("tables/Supplementary_Table_XXX__samplingDiffFormatDate.txt", sep="\t"))

# Annotated table with all data for the 99 selected and curated viral contigs
tv_ann_table_99c <- read_excel("tables/all99_gc_metad_annotated_quality.xlsx")

# Coverage stats at different thresholds for the 99 selected contigs
tv_cov_table_99c <- data.frame(read.csv("tables/allselected99tickvirome_breadth_depth.txt", sep="\t"))

# NCBI RefSeq viruses
ncbi_seqs_metadata <- data.frame(read.csv("tables/taxid10239.nbr", sep="\t"))

```

Figure 1a - Map Showing the obtained samples
```{r}
# Retrieve world geographic data, transform them in a raster and zoom on the area of interest
world <- ne_countries(scale = "large", returnclass = "sf")
world_spatial <- as_Spatial(world)
italy_raster <- raster(crs = crs(world), vals = 0, resolution = c(0.1, 0.1), ext = extent(c(6.3, 18.7, 36.5, 47.2))) %>% rasterize(world, .)

# Insert borders
borders = crop(getData("GADM", country="ITA", level=1), extent(italy_raster))
ita_borders <- st_as_sf(borders)

# Plot the whole area (Italy) - Minimal information
# Set colour palette - Use Wong's palette (https://www.nature.com/articles/nmeth.1618)
colfunc <- c('Trento'="#56B4E9", 'Lazio'="#009E73", 'Sicily'="#E69F00")

ggplot(data = world) +
    geom_sf(data = ita_borders, fill = "white", color="black", size=0.3) +
    geom_point(data = sample_stats, aes(x = Longitude, y = Latitude, color=Region), size = 2.5) +
    coord_sf(xlim = c(6.3, 18.7), ylim = c(36.5, 47.2), expand = FALSE)+
    theme(panel.grid.major = element_line(colour = "transparent"), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks.y=element_blank(), axis.title.x=element_blank(), axis.title.y=element_blank(), panel.border = element_blank(), legend.text=element_text(size=10))+
labs(color="Region")+scale_color_manual(values=colfunc, na.value="#000000")

```

Figure 1b - Heatmap showing RPKM (or RPM) for the identified viral families
```{r}
# Get the columns needed for the calculation of RPM and RPKM at family level
family_level_abundance <- tv_ann_table_99c %>% dplyr::select(sample,tick,region_province,family,tot_reads,mapreads_singlemap,Seq_length) %>%
group_by(sample, family) %>%
dplyr::summarise(mapreads_singlemap=sum(mapreads_singlemap), Seq_length=sum(Seq_length), sample=sample, tick=tick, region_province=region_province, tot_reads=tot_reads) %>% distinct()

# Calculate RPKM and RPM at the family level
tv_rpkm_family_df <- family_level_abundance %>% mutate(RPKM=mapreads_singlemap/((Seq_length/1000)*(tot_reads/1000000))) %>% mutate(RPM=1000000*(mapreads_singlemap/(tot_reads))) %>% mutate(logRPKM=log(RPKM)) %>% mutate(logRPM=log(RPKM))

# RPKM heatmap
tv_rpkm_tomatrix <- tv_rpkm_family_df %>% dplyr::select(sample, family, logRPKM)
tv_rpkm_tomatrix_df <- data.frame(tv_rpkm_tomatrix)
tv_rpkm_tomatrix_wide_df <- spread(tv_rpkm_tomatrix_df, family, logRPKM)

rownames(tv_rpkm_tomatrix_wide_df) <- tv_rpkm_tomatrix_wide_df[,1]
tv_rpkm_tomatrix_wide_df[,1] <- NULL
tv_rpkm_tomatrix_wide_df[is.na(tv_rpkm_tomatrix_wide_df)] <- 0

tv_rpkm_matrix <- as.matrix.data.frame(tv_rpkm_tomatrix_wide_df, rownames.force = TRUE)

# Hclust2 type palette
# c("black", "#0000ff","#00ffff","#ffffff","#ffff00")
HCcol_funRPKM = colorRamp2(c(0, 2.5, 5, 7.5, 10), c("black", "#0000ff","#00ffff","#ff0000","#ffff00"))

# Red-black palette
#col_funRPKM = colorRamp2(c(0, 5, 10), c("black", "yellow", "red"))
#col_funRPM = colorRamp2(c(0, 6, 12), c("black", "yellow", "red"))

Heatmap(t(tv_rpkm_matrix), cluster_columns=FALSE, show_row_dend = FALSE, cluster_row_slices = FALSE, cluster_column_slices = FALSE, name="logRPKM", col=HCcol_funRPKM)

# Add annotation

# Annotation
# Get the original order of the matrix
# Column
original_order <- data.frame(colnames(t(tv_rpkm_matrix)))
colnames(original_order) <- c('Sample')
row_id2 <- seq(1, nrow(original_order))
original_order$row_id2 = row_id2

# Rows
#original_order_rows <- data.frame(rownames(t(tv_rpkm_matrix)))
#colnames(original_order_rows) <- c('Sample')
#roW_id2 <- seq(1, nrow(original_order_rows))
#original_order_rows$row_id2 = roW_id2
#row_forder = order(tv_rpkm_family_df$family)  # Get the order of rows alphabetically
#data_ordered = data[row_order, ]  # Reorder the data according to the alphabetical order of rows

annfamhtmp <- data.frame(sample_stats$Species, sample_stats$Region, sample_stats$sample)

colnames(annfamhtmp) <- c('Species', 'Region', 'Sample')
row_id <- seq(1, nrow(annfamhtmp))
annfamhtmp$row_id = row_id

annfamhtmpORD <- data.frame(annfamhtmp[order(annfamhtmp$Species, annfamhtmp$Region, annfamhtmp$Sample),])
annfamhtmpORDred <- annfamhtmpORD %>% dplyr::select(Species, Region)

colours <- list('Species' = c('Ixodes ricinus' = '#0072b2', 'Dermacentor marginatus' = '#d55e00','Haemaphysalis punctata'='#cc79a7','Rhipicephalus bursa'='#000000','Rhipicephalus sanguineus'='#f0e442'), 'Region' = c('Trento'="#56B4E9", 'Lazio'="#009E73", 'Sicily'="#E69F00"))

colAnn <- HeatmapAnnotation(df = annfamhtmpORDred,
  which = 'col',
  col = colours,
  annotation_width = unit(c(1, 4), 'cm'),
  gap = unit(1, 'mm'), gp = gpar(col = "black"))

final_order <- merge(original_order,annfamhtmpORD, by="Sample", all.x=TRUE)
final_orderS <- data.frame(final_order[order(final_order$Species,final_order$Region,final_order$Sample),])

column_order <- final_orderS$row_id2
ordered_data <- t(tv_rpkm_matrix)[, column_order]

Heatmap((ordered_data), cluster_columns=FALSE, cluster_rows=FALSE, show_row_dend = FALSE, cluster_row_slices = FALSE, cluster_column_slices = FALSE, name="logRPKM", col=HCcol_funRPKM, 
        top_annotation = colAnn)

```

Figure 1c - Alpha diversity for each sample
```{r}
# Get the columns needed for the calculation of RPM and RPKM at species level
species_level_abundance <- tv_ann_table_99c %>% dplyr::select(sample,tick,region_province,putative_species,tot_reads,mapreads_singlemap,Seq_length) %>%
group_by(sample, putative_species) %>%
dplyr::summarise(mapreads_singlemap=sum(mapreads_singlemap), Seq_length=sum(Seq_length), sample=sample, tick=tick, region_province=region_province, tot_reads=tot_reads) %>% distinct()

# Calculate RPKM, RPM and TPM at the species level
tv_rpkm_species_df <- species_level_abundance %>% mutate(RPKM=mapreads_singlemap/((Seq_length/1000)*(tot_reads/1000000))) %>% mutate(RPM=1000000*(mapreads_singlemap/(tot_reads))) %>% mutate(logRPKM=log(RPKM)) %>% mutate(logRPM=log(RPKM)) %>% mutate(NiLi=mapreads_singlemap/Seq_length)

tv_rpkm_NnLn_species_df <- tv_rpkm_species_df %>% group_by(sample) %>% dplyr::summarise(sample=sample, putative_species=putative_species, region_province=region_province, tick=tick, mapreads_singlemap=mapreads_singlemap, Seq_length=Seq_length, NiLi=NiLi, NnLn=sum(NiLi)) %>% distinct() 

tv_rpkm_TPM_species_df <- tv_rpkm_NnLn_species_df %>% 
  mutate(TPM=((mapreads_singlemap/Seq_length)*(1000000))/(NnLn))

# Get table to calculate alpha diversity using TPM values
tv_species_alphaD_df <- tv_rpkm_TPM_species_df %>% dplyr::select(sample, putative_species, TPM, region_province)

# Calculate alpha-diversity
tv_species_alphaD_plot_df <- tv_species_alphaD_df %>% 
  group_by(sample) %>%
  summarise(shannon = shannon(TPM),
            simpson1 = simpson(TPM),
            simpson = 1/simpson1) %>%
  pivot_longer(cols=c(shannon, simpson), names_to = "metric")
# Add other indices to summarise:
# sobs = richness(TPM)
# invsimpson = 1/simpson
# Add to pivot longer:
# cols=c(sobs, invsimpson) 

tv_species_alphaD_plot_stats_df <- merge(tv_species_alphaD_plot_df, sample_stats)

# Plot alpha diversity measures by species
colfunc_species=c('Dermacentor marginatus' = '#d55e00','Haemaphysalis punctata'='#cc79a7','Ixodes ricinus' = '#0072b2','Rhipicephalus bursa'='#000000','Rhipicephalus sanguineus'='#f0e442')
colfunc_ticks=c('D. marginatus' = '#d55e00','H. punctata'='#cc79a7','I. ricinus' = '#0072b2','R. bursa'='#000000','R. sanguineus'='#f0e442')

alphaD_species_plot <- tv_species_alphaD_plot_stats_df %>% 
  ggplot(aes(x = reorder_within(Tick, value, metric, median), y = value, color=Tick, fill=Tick)) +
  geom_boxplot(alpha=0.2)+
  geom_violin(alpha=0.2,trim=FALSE)+
  geom_point(alpha=1,size=1.5)+
  scale_x_reordered()+
  theme(panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.text.x = element_text(angle = 45, vjust = 1.0, hjust=1.02, face = "italic"), axis.title.x=element_blank())+
  facet_wrap(vars(metric), scales = "free", labeller = metric_labeller)+
  scale_color_manual(values=colfunc_ticks, na.value="#000000")+
  scale_fill_manual(values=colfunc_ticks, na.value="#000000")

# Statistics
tv_species_alphaD_shannon <- tv_species_alphaD_plot_stats_df %>% filter(metric=="shannon")
tv_species_alphaD_simpson <- tv_species_alphaD_plot_stats_df %>% filter(metric=="simpson")

kruskal.test(value ~ Species, data = tv_species_alphaD_shannon)
kruskal.test(value ~ Species, data = tv_species_alphaD_simpson)

pairwise.wilcox.test(tv_species_alphaD_shannon$value, tv_species_alphaD_shannon$Tick, p.adjust.method = "bonferroni")
pairwise.wilcox.test(tv_species_alphaD_simpson$value, tv_species_alphaD_shannon$Tick, p.adjust.method = "bonferroni")
  
# Plot alpha diversity measures by region
colfunc_regions <- c('Trento'="#56B4E9", 'Lazio'="#009E73", 'Sicily'="#E69F00")
alphaD_regions_plot <- tv_species_alphaD_plot_stats_df %>% 
  ggplot(aes(x = reorder_within(Region, value, metric, median), y = value, color=Region, fill=Region)) + 
  geom_boxplot(alpha=0.2)+
  geom_violin(alpha=0.2,trim=FALSE)+
  geom_point(alpha=1,size=1.5)+
  scale_x_reordered()+
  facet_wrap(vars(metric), scales = "free", labeller = metric_labeller)+
  theme(panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.title.x=element_blank())+
  scale_color_manual(values=colfunc_regions, na.value="#000000")+
  scale_fill_manual(values=colfunc_regions, na.value="#000000")

# Statistics
tv_species_alphaD_shannon <- tv_species_alphaD_plot_stats_df %>% filter(metric=="shannon")
tv_species_alphaD_simpson <- tv_species_alphaD_plot_stats_df %>% filter(metric=="simpson")

kruskal.test(value ~ Region, data = tv_species_alphaD_shannon)
kruskal.test(value ~ Region, data = tv_species_alphaD_simpson)

pairwise.wilcox.test(tv_species_alphaD_shannon$value, tv_species_alphaD_shannon$Region, p.adjust.method = "bonferroni")
pairwise.wilcox.test(tv_species_alphaD_simpson$value, tv_species_alphaD_shannon$Region, p.adjust.method = "bonferroni")

plot_grid(alphaD_species_plot, alphaD_regions_plot, labels = "AUTO", ncol = 1, align=c("hv"))
```

Supplementary Figure 1 - Heatmap showing RPKM (or RPM) for the identified viral species
```{r}
# Get the columns needed for the calculation of RPM and RPKM at family level
species_level_abundance <- tv_ann_table_99c %>% dplyr::select(sample,tick,region_province,putative_species,tot_reads,mapreads_singlemap,Seq_length) %>%
group_by(sample, putative_species) %>%
dplyr::summarise(mapreads_singlemap=sum(mapreads_singlemap), Seq_length=sum(Seq_length), sample=sample, tick=tick, region_province=region_province, tot_reads=tot_reads) %>% distinct()

# Calculate RPKM and RPM at the family level
tv_rpkm_species_df <- species_level_abundance %>% mutate(RPKM=mapreads_singlemap/((Seq_length/1000)*(tot_reads/1000000))) %>% mutate(RPM=1000000*(mapreads_singlemap/(tot_reads))) %>% mutate(logRPKM=log(RPKM)) %>% mutate(logRPM=log(RPKM))

# RPKM heatmap
tv_rpkm_tomatrix <- tv_rpkm_species_df %>% dplyr::select(sample, putative_species, logRPKM)
tv_rpkm_tomatrix_df <- data.frame(tv_rpkm_tomatrix)
tv_rpkm_tomatrix_wide_df <- spread(tv_rpkm_tomatrix_df, putative_species, logRPKM)

rownames(tv_rpkm_tomatrix_wide_df) <- tv_rpkm_tomatrix_wide_df[,1]
tv_rpkm_tomatrix_wide_df[,1] <- NULL
tv_rpkm_tomatrix_wide_df[is.na(tv_rpkm_tomatrix_wide_df)] <- 0

tv_rpkm_matrix <- as.matrix.data.frame(tv_rpkm_tomatrix_wide_df, rownames.force = TRUE)

# Hclust2 type palette
# c("black", "#0000ff","#00ffff","#ffffff","#ffff00")
HCcol_funRPKM = colorRamp2(c(0, 2.5, 5, 7.5, 10), c("black", "#0000ff","#00ffff","#ff0000","#ffff00"))

# Red-black palette
#col_funRPKM = colorRamp2(c(0, 5, 10), c("black", "yellow", "red"))
#col_funRPM = colorRamp2(c(0, 6, 12), c("black", "yellow", "red"))

Heatmap(t(tv_rpkm_matrix), cluster_columns=FALSE, show_row_dend = FALSE, cluster_row_slices = FALSE, cluster_column_slices = FALSE, name="logRPKM", col=HCcol_funRPKM)

# Add annotation

# Annotation
# Get the original order of the matrix
# Column
original_order <- data.frame(colnames(t(tv_rpkm_matrix)))
colnames(original_order) <- c('Sample')
row_id2 <- seq(1, nrow(original_order))
original_order$row_id2 = row_id2

# Rows
#original_order_rows <- data.frame(rownames(t(tv_rpkm_matrix)))
#colnames(original_order_rows) <- c('Sample')
#roW_id2 <- seq(1, nrow(original_order_rows))
#original_order_rows$row_id2 = roW_id2
#row_forder = order(tv_rpkm_family_df$family)  # Get the order of rows alphabetically
#data_ordered = data[row_order, ]  # Reorder the data according to the alphabetical order of rows

annfamhtmp <- data.frame(sample_stats$Species, sample_stats$Region, sample_stats$sample)

colnames(annfamhtmp) <- c('Species', 'Region', 'Sample')
row_id <- seq(1, nrow(annfamhtmp))
annfamhtmp$row_id = row_id

annfamhtmpORD <- data.frame(annfamhtmp[order(annfamhtmp$Species, annfamhtmp$Region, annfamhtmp$Sample),])
annfamhtmpORDred <- annfamhtmpORD %>% dplyr::select(Species, Region)

colours <- list('Species' = c('Ixodes ricinus' = '#0072b2', 'Dermacentor marginatus' = '#d55e00','Haemaphysalis punctata'='#cc79a7','Rhipicephalus bursa'='#000000','Rhipicephalus sanguineus'='#f0e442'), 'Region' = c('Trento'="#56B4E9", 'Lazio'="#009E73", 'Sicily'="#E69F00"))

colAnn <- HeatmapAnnotation(df = annfamhtmpORDred,
  which = 'col',
  col = colours,
  annotation_width = unit(c(1, 4), 'cm'),
  gap = unit(1, 'mm'), gp = gpar(col = "black"))

final_order <- merge(original_order,annfamhtmpORD, by="Sample", all.x=TRUE)
final_orderS <- data.frame(final_order[order(final_order$Species,final_order$Region,final_order$Sample),])

column_order <- final_orderS$row_id2
ordered_data <- t(tv_rpkm_matrix)[, column_order]

Heatmap((ordered_data), cluster_columns=FALSE, cluster_rows=FALSE, show_row_dend = FALSE, cluster_row_slices = FALSE, cluster_column_slices = FALSE, name="logRPKM", col=HCcol_funRPKM, 
        top_annotation = colAnn)

```

Supplementary Figure 2 - Breadth and depth of coverage for different quality thresholds
```{r}
plotSupp1a_mapping_quality_stats <- ggplot(tv_cov_table_99c, aes(x=breadth, y=log(depthavg), color=breadth,fill= breadth)) +
  geom_point(alpha=0.8,size=1.5) + ylim(-0.1,10)+ xlim(0,1) + #position=position_jitter(width=0.15), 
  geom_boxplot(fill=NA, outlier.size=NA,lwd=1) + guides(fill=FALSE) +
  ylab("Log average coverage depth") + 
  xlab("Breadth of coverage") + 
  geom_violin(alpha=0.3,trim=FALSE) + 
  facet_grid(. ~ mincov, scales = "free_x", space="free_x") +
  facet_grid(~factor(mincov, levels=c('nofilter', 'mincov3', 'mincov5', 'mincov10')))+
  theme_light() +
  theme(legend.position="none") + 
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank())

plotSupp1b_mapping_quality_stats <- ggplot(tv_cov_table_99c, aes(x=breadth, y=log(depthmedian), color=breadth,fill= breadth)) +
  geom_point(alpha=0.8,size=1.5) + ylim(-0.1,10)+ xlim(0,1) + #position=position_jitter(width=0.15), 
  geom_boxplot(fill=NA, outlier.size=NA,lwd=1) + guides(fill=FALSE) +
  ylab("Log median coverage depth") + 
  xlab("Breadth of coverage") + 
  geom_violin(alpha=0.3,trim=FALSE) + 
  facet_grid(. ~ mincov, scales = "free_x", space="free_x") +
  facet_grid(~factor(mincov, levels=c('nofilter', 'mincov3', 'mincov5', 'mincov10')))+
  theme_light() +
  theme(legend.position="none") + 
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank())

plot_grid(plotSupp1a_mapping_quality_stats, plotSupp1b_mapping_quality_stats, labels = "AUTO", ncol = 1)

```

Supplementary Figure 3 - Viral phylogeny at the family level
```{r}
ncbi_seqs_metadata2 <- ncbi_seqs_metadata %>% separate(SelectedLineage, into=c("family","genus","species"), sep="[,]", remove=FALSE)


botourmiaviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Botourmiaviridae")
bromoviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Bromoviridae")
chuviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Chuviridae")
circoviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Circoviridae")
flaviviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Flaviviridae")
luteoviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Luteoviridae")
nairoviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Nairoviridae")
orthomyxoviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Orthomyxoviridae")
partitiviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Partitiviridae")
peribunyaviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Peribunyaviridae")
phenuiviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Phenuiviridae")
rhabdoviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Rhabdoviridae")
totiviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Totiviridae")

virgaviridae_seqs <- ncbi_seqs_metadata2 %>% filter(family=="Virgaviridae")

putative_new_vspecies <- c("Bole Tick Mediterranean Virus","Circoviridae sp.","Inglesidevirus tarquiniae", "Lonestarticktotivirus italiae", "Mononegavirus tridentinum", "Tickbunyavirus siciliae", "Totiviridae sp.", "Totivirus genuardii", "Zambezi tick like italian virus")

putative_new_vspecies_family <- c("Chuviridae","Circoviridae","Virgaviridae","Totiviridae","Rhabdoviridae","Peribunyaviridae","Totiviridae","Totiviridae","Orthomyxoviridae")


## Too short to say something (then discarded from the list of new viruses) ##

# Circoviridae sp.: probably all contaminants
# RB-25T: only capsid protein

# Lonestar_tick_totivirus__RS-M1__pnv

# All Mononegavirus tridentinum contigs

# Xinjiang tick totivirus 2
# Xinjiang_tick_totivirus_2__DM-F3__pnv
# Xinjiang_tick_totivirus_2__DM-1T__kv
# Xinjiang_tick_totivirus_2__DM-26I__pnv
# Xinjiang_tick_totivirus_2__DM-F3__kv
# Xinjiang_tick_totivirus_2__RB-41T__pnv
# Xinjiang_tick_totivirus_2__DM-27I__pnv

# All Zambezi tick like italian virus


# Real new viruses
# Bole Tick Mediterranean Virus
# Inglesidevirus tarquiniae
# Lonestarticktotivirus italiae
# Tickbunyavirus siciliae
# Totivirus genuardii


```